Revisiting Multi-Domain Machine Translation

### 2020-09-02 2020/tacl2020/rebuttal.tex

\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
\newcommand{\system}[1]{\texttt{\textbf{#1}}}

\title{Responses to the reviews of TACL paper \#2327:
  ``Revisiting Multi-Domain Machine Translation''
}
\author{Action Editor: G. Foster}
\date{}

\begin{document}
\maketitle

\textcolor{blue}{The authors wish thank to the reviewers and editor for their comments and suggestions. We have tried to address their questions and concerns in the revised version. Details are given below, with pointers to the main changes in the text. Typos and presentations errors have also been corrected in the new submission.}

@@

\section*{Cover mail}
As TACL action editor for submission 2327, "Revisiting Multi-Domain Machine Translation", I am happy to tell you that I am accepting your paper subject (conditional) to your making specific revisions within two months.

Please address all comments by the reviewers, paying special attention to the following:
\begin{itemize}
\item Address the concern by reviewer~A about the difference between \system{MDL Res} and \system{FT-Block}, and include \system{FT-block} (and ideally \system{FT-Full} also) in the later experiments (5.2.2 and 5.3). \\
  \textcolor{blue}{The differences between these two systems is explained in our response to reviewer A below, and has lead us to substantially revise section 4.3 where we describe our multi-domain systems. As requested,  \system{FT-Block} has now been included in all the comparative evaluations. }
\item Carefully specify the number of parameters for all models, including the proportions that are domain-specific and domain-independent. \\
  \textcolor{blue}{These numbers now appear in the revised version of Table 3.}
\item Provide all the experimental details requested, and in particular give enough information to allow the corpora to be reproduced, or (ideally) make them publicly available.\\
  \textcolor{blue}{We have added an appendix devoted to the system details, giving all the necessary information regarding meta-parameter settings and training procedures. The exact split of train / dev / test data used in this study will be distributed together with the final version of the paper.}
\end{itemize}

@@

You are allowed one to two extra pages of content to accommodate these revisions. To submit your revised version, follow the instructions in the "Revision and Resubmission Policy for TACL Submissions" section of the
Author Guidelines at \url{https://transacl.org/ojs/index.php/tacl/about/submissions\#authorGuidelines}.

\textcolor{blue}{We have joint to this mail two versions of the revised paper: one where the main changes appear in red, and the appendix is placed before the references so has to highlight the differences with the first version; one version that looks like a regular submission. We hope that this will make it easier for reviewers to view the differences with the first version of the paper.}

@@

The large number of approaches considered is admirable. However, the depth of the discussion suffers as a consequence, and the paper risks making over-general statements about the weaknesses of different approaches, despite related work that has already addressed them. The authors conclude that fine-tuning "incurs large losses [when applied on] the small data condition", and fails to deteriorate gracefully in the presence of tag errors, issues that have been addressed by Miceli Barone et al. (2017) and Thompson et al. (2019), respectively. Similarly, the negative impact of adding data from a "new" domain seems slightly overblown. Firstly, this is probably highly dependent on data mixtures, length of training and regularization strategies, so I'd be wary of drawing general conclusions from a single set of experiments. Secondly, when looking at the models where such a performance deterioration is said to happen (\system{DC-Tag}, \system{TTM}, \system{ADM}; lines 770-771), this deterioration is actually small or non-existent when comparing table 3 and table 5 averages (-0.2 BLEU for \system{DC-Tag}; -0.3 BLEU for \system{TTM}; +0.9 BLEU for \system{ADM}).
\\
\textcolor{red}{%
  We have tried to address these comments in the revised version of the paper. Notably, we have clarified the distinction between \system{FT-block} and \system{MDL Res} (see details below). We have also tried to clarify the distinction between multi-domain MT and fine-tuning; while the former is designed given the (mono-domain) test data distribution, the latter assumes that the test data will be sampled from multiple domains, using domain probabilities that are not known in advance. This raises the issues of robustness with respect to adversarial test distribution and even new domains, two issues that are somewhat irrelevant for DA.
\newline

@@

    \\
    To train MDL res, we optimize the parameters of the Transformer model and the parameters of the residual adapters from scratch. More precisely, to create a training batch, we randomly pick a domain with a probability equal to the proportion of the domain in training data, then sample a batch from the corresponding corpus. Given a batch from domain $i$, we simultaneously optimize the parameters of Transformer model and the parameters of the residual adapters for that domain.
    \\
    We understand that our naming schemes was insisting on training procedures, rather than on architectures, thus possibly introducing some confusions. We have accordingly changed the name of \system{FT-Block} to \system{FT Res}, clarified the description of the two systems (see lines YYY\fyTodo{fix this}), and reported \system{FT-Res}\fyDone{or new name} as another multi-domain system in all tables.\fyTodo{Make sure it is the case}.}

@@

  %}
\end{itemize}

\noindent\textbf{Minor issues:}
\begin{itemize}
\item I disagree that generalization to unseen domains is similar to zero-shot multilingual MT. In zero-shot multilingual MT, both the source and target distribution have been observed at training time, just paired with other languages. In the generalization to unseen domains, there may be characteristics in the data that were never seen in the training data, including new vocabulary (in the source text, target text, or both).
  \\
  \textcolor{blue}{We agree with the reviewer that the analogy is misleading. As this is not central to our discussion, we have rephrased and dropped the comparison. See changes in line XXX}\fyTodo{Changes line in.}
\item 567-568: "having the domain tag on the source is better than on the target". I assume this refers to the comparison of "DC-Tag" and "TTM". However, TTM actually uses the predicted domain label on the target side and could perform better with forced decoding of the gold domain label. More precisely, the statement should be that "having the gold tag is better than a predicted tag", but this is hardly surprising.
  \\
  \textcolor{blue}{We agree that the conclusion is not really fair for "TTM" because "TTM" intend to predict domain label rather than to use gold domain label and TTM could definitively translate with gold domain label as prefix of each hypothesis. In our experiments, we found that TTM is pretty accurate in its prediction, making about 2\% errors in the predicted tags, which may explain the small difference with observe in Table~3. We have rephrased acccordingly in lines WWW.}\fyTodo{Add lines}
\end{itemize}

\section*{Reviewer B}
The paper presents a thorough review of Multi-Domain Machine Translation (MDMT) approaches, and the authors provide comprehensive experiments to study different aspects of MDMT. The innovation of this work can be seen in two main categories:
\begin{itemize}
\item suggesting a methodology to evaluate MDMT models based on seven properties that they defined in the paper.
\item empirical studies on eight recent MTMD approaches.
\end{itemize}
In general, the paper has written well, and it is a good read for those who are researching in the domain adaptation field. 
\\
I have a few comments:
\\
\begin{itemize}
\item[*] You provide some useful experimental results on various MDMT approaches. To benefit from your results, we need access to the same segmentation of train/dev/test sets that I hope you will provide to the community.
\textcolor{blue}{Supplementary details regarding the settings used in our experiments have been added in a new Appendix YYY.\fyTodo{Fix the appendix.}. We will also distribute the detailed composition of our train / dev / test split upon acceptance of the paper.}
\\
\item[*] On your discussion on the number of parameters (L. 591), could you share the number of parameters per each MDMT approach~? It will be helpful to see  the impact of the number of parameters on the MT results.
  \textcolor{blue}{This information has been added in Table~3\fyTodo{Check number, page and line number and content}.}
\\ 
\item[*] Thinking about your seven operational requirements, I wonder if you could also define a domain or the minimum number of samples to specify a domain. I like your selections of domains that you include multiple domains with varying sizes, but what we expect in extreme cases. Having your Split experiments on REL (Table 4), or providing further details on your last analysis in Section 5.3, if you have tiny clusters could help.\fyTodo{Answer this with more experiments ?}
  \\
  \textcolor{blue}{We agree that carefully analyzing the effects of using corpora of varying size is important, as this corresponds to practical training scenario. From our results in Table 7 (and Table 8 in Appendix B), we see that some techniques can work well with small in-domain corpora. However, this analysis must also take in account the similarity between domains, as these improvements will be stronger if similar or related data are also present in the training mixture -- a situation that we have artificially created in our split conditions. Precisely sorting out these two effects is beyond the scope of this study and left for future work.}

@@

\item[*] L. 687: Please describe how you predict the domain tag, and please share the tag prediction error rate on each domain test set. It is helpful to see the amount and the impact of the error on MDMT results.
\\
\textcolor{blue}{We train a language model in source language for each domain using the corresponding training corpus. To predict the domain tag of a sentence, we compute the probability of the sentence according to each pretrained language model and choose the domain having the highest probability as the domain tag for that sentence. Note that this classifier is only used for the \domain{news} test data. This is now explained in footnote ZZZ.}\fyTodo{to compute error rate of domain prediction over each test set, check comment, add footnote number.}
\end{itemize}

@@

\\
\item Maybe the (possible) effect of early stopping (and the choice of the validation set) should be discussed~? E.g., the validation set for finetuning can originate from one single domain for each finetuned model. The way you're doing early stopping may even have had an impact on the results in Table 5. Is your validation set always a concatenation of 1000 lines from the six domains, without NEWS~? Are you actually always training until the early stopping criterion is reached, and are you then using the model from the best checkpoint? (There are contradictory statements in the paper about "50,000  additional iterations" (?) for the experiments in Table 5.)
\\
\textcolor{red}{For each domain, we create train/dev/test sets by randomly splitting each corpus. We maintain the size of validation sets and of test sets equal to 1,000 lines for every domain. In Tables 3 and 4, to train MDMT systems (except FT-full and FT Res), we use a validation set which is a concatenation of the 6 validation sets of 6 domains. In Table 5, to train MDMT systems (except \system{FT-Full} and \system{FT Res}) we append the validation set of \domain{news} to the concatenation of 6 validation sets. To train \system{FT-full} and \system{FT Res} model we only use the in-domain validation sets. We stop training if either the training iteration reach the maximal number of iterations or the score on the validation set does not increase in 3 consecutive evaluations. We average 5 checkpoints preceding the best checkpoint to get the final model. All these details are in Appendix B}\fyDone{up to the best ?}

### 2020-09-02 2020/tacl2020/multidomain.tex

\subsection{Multi-domain systems \label{ssec:systems}}
\fyDone{Remove Gated residual}
Our comparison of multi-domain systems includes our own reimplementations of recent proposals from the literature:\footnote{\revision{Further implementation details are in Appendix~A.}}
\begin{itemize}
\item a system using domain control as in \cite{Kobus17domaincontrol}: domain information is introduced either as an additional token for each source sentence (\system{DC-Tag}), or as a supplementary feature for each word (\system{DC-Feat}).
\item a system using lexicalized domain representations \cite{Pham19generic}: word embeddings are composed of a generic and a domain specific part (\system{LDR});\fyDone{why not LDR as in Minh's paper?}
\item the three proposals of \newcite{Britz17mixing}. \system{TTM} is a feature-based approach where the domain tag is introduced as an extra word \textsl{on the target side}. Training uses reference tags and inference is usually performed with predicted tags, just like for regular target words. \system{DM} is a multi-task learner where a domain classifier is trained on top the MT encoder, so as to make it aware of domain differences; \system{ADM} is the adversarial version of \system{DM}, pushing the encoder towards learning domain-independent source representations. These methods thus only use domain tags in training.
\item the multi-domain model of \newcite{Zeng18multidomain} (\system{WDCMT}), where a domain-agnostic and a domain-specialized representation of the input are simultaneously processed; supervised classification and adversarial training are used to compute these representations. \revision{Again, inference does not use domain tags.}\footnote{For this system, we use the available RNN-based system from the authors (\url{https://github.com/DeepLearnXMU/WDCNMT}\fyDone{URLs}) which does not directly compare to the other, Transformer-based, systems; the improved version of \cite{Su19exploring} seems to produce comparable, albeit slightly improved, results.}\fyDone{Check this}
\item \revision{two multi-domain versions of the approach of \newcite{Bapna19simple}, denoted \system{FT-Res} and \system{MDL-Res}, where a domain-specific adaptation module is added to all the Transformer layers; within each layer, residual connections enable to by-pass this module. The former variant corresponds to the original proposal of \citet{Bapna19simple} \revision{(see also \cite{Sharaf20metalearning})}. It fine-tunes the adapter modules of a \system{Mixed-Nat} system independently for each domain, keeping all the other parameters frozen. The latter uses the same architecture, but a different training procedure and learns all parameters jointly from scratch with a mix-domain corpus.}
  % In a variant (\system{MDL Gated}), we use a gating mechanism to merge computations using the the adapter modules and with those that don not.
% the entire multi-domain system from scratch.\fyDone{Check this.}
\end{itemize}
\revision{This list includes systems that slightly depart from our definition of MDMT: standard implementations of \system{TTM} and \system{WDCMT} rely on infered, rather than on gold, domain tags - which must somewhat affect their predictions; \system{DM} and {ADM} make no use of domain tags at all.} We however did not consider the proposal of \cite{Farajian17multidomain} which performs on-the-fly tuning for each test sentence and diverges more strongly from our notion of MDMT. % and should be able to handle available domain labels in training and testing.
% This system has shown to meet several of requirements and would also have no problem scaling to a large number of domains.\fyDone{TBC}

@@

\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
    \system{Mixed-Nat}  \hfill{\footnotesize[65m]} & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
    \system{Mixed-Bal}   \hfill{\footnotesize[65m]} &  35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5 & 40.3  & 51.4 \\ %& \\
    \system{FT-Full}       \hfill{\footnotesize[6$\times$65m]} & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & \SB{42.7} & \SB{53.8} \\ \hline
 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag} \hfill{\footnotesize[+4k]}        & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & \SB{80.5} &41.6 & 50.1    \\%    & 21.8 \\
    \system{DC-Feat} \hfill{\footnotesize[+140k]}    & 37.7  & 54.9 & 49.5   & 32.9 & 43.6 & \SB{79.9} &41.4 & 49.9   \\% & \SW{21.7} \\
    \system{LDR}       \hfill{\footnotesize[+1.4m]}    & 37.0   & 54.7 & 49.9 & 33.9 & 43.6 & \SB{79.9} &40.9 & 49.8          \\% & 22.1 \\ 
    \system{TTM}      \hfill{\footnotesize[+4k]}        & 37.3 & 54.9 & 49.5 & 32.9 & 43.6 & \SB{79.9} &41.0 & 49.7     \\% &  23.4 \\
    \system{DM}        \hfill{\footnotesize[+0]}         & \SW{35.6} & \SW{49.5}  & \SW{45.6}& \SW{29.9} & \SW{37.1} & \SW{62.4} & 38.1 & 43.4 \\ % & 22.6\\
    \system{ADM}      \hfill{\footnotesize[+0]}         & 36.4 & \SW{53.5}  & \SW{48.3} & \SW{32.0} & \SW{41.5} & \SW{73.4} & 38.9 & 47.5 \\% & 23.3 \\
    \revision{\system{FT-Res}}   \hfill{\footnotesize[+12.4m]}  & 37.3 & \SB{57.9} & \SB{53.9} & 33.8 & \SB{46.7} & \SB{90.2}  & \SB{42.3} & \SB{53.3} \\ % & 20.5\\ \hline
    \system{MDL-Res} \hfill{\footnotesize[+12.4m]}    & 37.9 & \SB{56.0}  & \SB{51.2}   & 33.5   &  44.4  & \SB{88.3} & 42.0 & \SB{51.9} \\%  & \SW{21.2} \\
%     \hfill MDL Res (gen)    & 37.7 & 51.0 & 34.0 & 30.4 & 34.2 & 15.2 & 36.4 & 33.7\\
%    \system{MDL Gated} & 37.7 & 56.5 & 53.2 & 34.1 & 44.6 & 90.7 & 42.3 & 53.3&\\
     \hline \hline
    \system{Mixed-Nat-RNN}  & 36.8 & 53.8 & 47.2 & 30.0 & 35.7 & 60.2  & 39.2  & 44.0 \\
    \hline
    \system{WDCMT}       & 36.0 & 53.3 & \SB{48.8} & 31.1 & \SB{38.8} & \SW{58.5} & 39.0 & 44.4 \\ % & 20.4 \\
    \hline
  \end{tabular}
  \caption{Translation performance of various MDMT systems \revision{based on the same Transformer (top) or RNN (bottom) architecture. The former contains 65m parameters, the latter has ???. For each system, we report the number of domain specific parameters,}  BLEU scores for each domain, as well as domain-weighted (w\domain{avg}) and unweighted (\domain{avg}) averages. \revision{In the former case, we take the domain proportions from Table~\ref{tab:Corpora}}. Boldface denotes significant gains with respect to \system{Mix-Nat} (or \system{Mix-Nat-RNN}, for WDCMT), underline denotes significant losses.}
  \label{tab:performance}
  % \fyDone{Fill the table with all results, including a comparison with *RNNs* for wcmd}
  \fyDone{Do we have significancy tests for averages?} %\fyTodo{Add tests wrt to RNN}
\end{table*}

@@

All MDMTs (except \system{DM} and \system{ADM}) slightly improve over \system{Mixed-Nat}(for most domains), but these gains are rarely significant. \revision{Among systems using an extra domain feature, \system{DC-Tag} has a small edge over \system{DC-Feat} and also requires less paramaters; it also outperforms \system{TTM}, which however uses predicted rather than gold domain tags. \system{TTM} is also the best choice among the systems that to not use domain tags in inference.} \revision{The best contenders overall are  \system{FT-Res} and \system{MDL-Res}, which significantly improve over \system{Mixed-Nat} for a majority of domains, and are the only ones to clearly fulfill [P1-LAB];} \system{WDCMT} also improves on three domains, but regresses on one. The use of a dedicated adaptation component, seems here better than feature-based strategies, \revision{but yields a large increase of the number of parameters.} The effect of the adaptation layer is especially significant for small domains (\domain{bank}, \domain{it} and \domain{rel}).

@@

\begin{table*}
  \centering% \small
  \begin{tabular}{|p{1.8cm}|*{10}{r|}} \hline
    % &&&&&& \\
    \hfill Set-up & \multicolumn{2}{c|}{Split} &  \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Merge} & \multicolumn{2}{c|}{Wrong} \\ % \hline
     Model \hfill & \multicolumn{2}{c|}{\domain{med} \footnotesize{(0.5 / 0.5)}} &  \multicolumn{2}{c|}{\domain{med} {\footnotesize (0.25 / 0.75)}} & \multicolumn{2}{c|}{\domain{law} {\footnotesize (0.5 / 0.5)}} & \multicolumn{2}{c|}{\domain{bank}+\domain{law}} &  \multicolumn{1}{c|}{\domain{rnd}} &  \multicolumn{1}{c|}{\domain{new}}\\ \hline
    & \domain{med}$_1$ & \domain{med}$_2$ & \domain{med}$_1$ & \domain{med}$_2$ &  \domain{bank}$_1$ & \domain{bank}$_2$ & \domain{bank} & \domain{law}   & \domain{all} & \domain{News} \\
    \system{FT-Full}      & -0.1 & -0.6 & \SW{-1.5} & -0.2& \SW{-2.3} & \SW{-5.1} &\SW{-1.6} & \SW{-1.4}& \SW{-19.6} & \SW{-3.3}\\% [32.5]
    \system{DC-Tag}     & -0.2 & -0.3& +\SB{0.1}  & +0.2& -0.4 & -0.4 & -0.5 & -0.4 & \SW{-13.4} & \SW{-1.7}\\% [35.9]
    \system{DC-Feat}    & -0.5 & 0.0 & +\SB{0.3}   & +0.3 & +0.3 & +0.3 & \textcolor{blue}{+}0.3 & +0.1 & \SW{-14.2} &\SW{-1.8}\\ % [34.9] 
    \system{LDR}           & +0.1 & +0.1 & +0.4 & +0.4 & 0.0 &  0.0 &  0.0 & +0.1& \SW{-12\textcolor{blue}{.0}} & \SW{-1.4}\\ % [37.0]
    \system{TTM} (*)        & -0.2 &  -0.2 & -0.2 & -0.2 & -0.3 &-0.3 &  0.0 & -0.3 & 0.0 & -0.1\\
%    \system{MDL Gated} & & & & & & & & &  \\
    \system{DM} (*)           & -0.3   & -0.3  & +0.4 & +0.4 & +0.3 & +0.3 & +0.9 & +0.1 & 0.0 &-0.9\\
    \system{ADM} (*)        & +0.6   & +0.6 & +0.4 & +0.4 & +0.4 & +0.4 &  +0.1 & -0.4 & 0.0&-0.2\\
    \revision{\system{FT-Res}}   & -0.1   & -0.4 & -0.3 &-0.3 & \SW{-2.2} & \SW{-2.9} & \SW{-2.4} & -\SW{3.2} & \SW{-13.3} & \SW{-3.0}\\ % [31.8]
    \system{MDL-Res}   & -0.2   & -0.1 & +\SB{0.2} &+0.0 & -0.9 & -0.9 & +0.7 & -0.3 & \SW{-18.6} & \SW{-1.3}\\ % [31.8]
    \system{WDCMT} (*)     & -0.0    & -0.0  & +0.2 & +0.2  & +0.8 & +0.8  & -0.4 & -0.8 & 0.0 & +0.2 \\
    \hline
  \end{tabular}
  \caption{Translation performance with variable domain definitions. In the Split/Merge experiments, we report BLEU differences for the related test set(s). Underline denotes significant loss when domains are changed wrt.\ the baseline situation; bold for a significant improvement over \system{FT-Full}; (*) tags systems ignoring test domains.
    \fyDone{Check wrong and significance of diff for ``old''}\fyDone{How about wrong ?}\jcTodo{FTres results are odd... split LAW 0.5}
  }
  \label{tab:redomains}
\end{table*}

>>>>

\subsection{Multi-domain systems \label{ssec:systems}}
\fyDone{Remove Gated residual}
Our comparison of multi-domain systems includes our own reimplementations of recent proposals from the literature:\footnote{\revision{Further implementation details are in Appendix~A.}}
\begin{itemize}
\item a system using domain control as in \cite{Kobus17domaincontrol}: domain information is introduced either as an additional token for each source sentence (\system{DC-Tag}), or as a supplementary feature for each word (\system{DC-Feat}).
\item a system using lexicalized domain representations \cite{Pham19generic}: word embeddings are composed of a generic and a domain specific part (\system{LDR});\fyDone{why not LDR as in Minh's paper?}
\item the three proposals of \newcite{Britz17mixing}. \system{TTM} is a feature-based approach where the domain tag is introduced as an extra word \textsl{on the target side}. Training uses reference tags and inference is usually performed with predicted tags, just like for regular target words. \system{DM} is a multi-task learner where a domain classifier is trained on top the MT encoder, so as to make it aware of domain differences; \system{ADM} is the adversarial version of \system{DM}, pushing the encoder towards learning domain-independent source representations. These methods thus only use domain tags in training.
\item the multi-domain model of \newcite{Zeng18multidomain} (\system{WDCMT}), where a domain-agnostic and a domain-specialized representation of the input are simultaneously processed; supervised classification and adversarial training are used to compute these representations. \revision{Again, inference does not use domain tags.}\footnote{For this system, we use the available RNN-based system from the authors (\url{https://github.com/DeepLearnXMU/WDCNMT}\fyDone{URLs}) which does not directly compare to the other, Transformer-based, systems; the improved version of \cite{Su19exploring} seems to produce comparable, albeit slightly improved, results.}\fyDone{Check this}
\item \revision{two multi-domain versions of the approach of \newcite{Bapna19simple}, denoted \system{FT-Res} and \system{MDL-Res}, where a domain-specific adaptation module is added to all the Transformer layers; within each layer, residual connections enable to short-cut this adapter. The former variant corresponds to the original proposal of \citet{Bapna19simple} \revision{(see also \cite{Sharaf20metalearning})}. It fine-tunes the adapter modules of a \system{Mixed-Nat} system independently for each domain, keeping all the other parameters frozen. The latter uses the same architecture, but a different training procedure and learns all parameters jointly from scratch with a mix-domain corpus.}
  % In a variant (\system{MDL Gated}), we use a gating mechanism to merge computations using the the adapter modules and with those that don not.
% the entire multi-domain system from scratch.\fyDone{Check this.}
\end{itemize}
\revision{This list includes systems that slightly depart from our definition of MDMT: standard implementations of \system{TTM} and \system{WDCMT} rely on infered, rather than on gold, domain tags - which must somewhat affect their predictions; \system{DM} and {ADM} make no use of domain tags at all.} We however did not consider the proposal of \cite{Farajian17multidomain} which performs on-the-fly tuning for each test sentence and diverges more strongly from our notion of MDMT. % and should be able to handle available domain labels in training and testing.
% This system has shown to meet several of requirements and would also have no problem scaling to a large number of domains.\fyDone{TBC}

@@

\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{4cm}|*{8}{r|}} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
    \system{Mixed-Nat}  \hfill{\footnotesize[65m]} & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
    \system{Mixed-Bal}   \hfill{\footnotesize[65m]} &  35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5 & 40.3  & 51.4 \\ %& \\
    \system{FT-Full}       \hfill{\footnotesize[6$\times$65m]} & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & \SB{42.7} & \SB{53.8} \\ \hline
 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag} \hfill{\footnotesize[+4k]}        & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & \SB{80.5} &41.6 & 50.1    \\%    & 21.8 \\
    \system{DC-Feat} \hfill{\footnotesize[+140k]}    & 37.7  & 54.9 & 49.5   & 32.9 & 43.6 & \SB{79.9} &41.4 & 49.9   \\% & \SW{21.7} \\
    \system{LDR}       \hfill{\footnotesize[+1.4m]}    & 37.0   & 54.7 & 49.9 & 33.9 & 43.6 & \SB{79.9} &40.9 & 49.8          \\% & 22.1 \\ 
    \system{TTM}      \hfill{\footnotesize[+4k]}        & 37.3 & 54.9 & 49.5 & 32.9 & 43.6 & \SB{79.9} &41.0 & 49.7     \\% &  23.4 \\
    \system{DM}        \hfill{\footnotesize[+0]}         & \SW{35.6} & \SW{49.5}  & \SW{45.6}& \SW{29.9} & \SW{37.1} & \SW{62.4} & 38.1 & 43.4 \\ % & 22.6\\
    \system{ADM}      \hfill{\footnotesize[+0]}         & 36.4 & \SW{53.5}  & \SW{48.3} & \SW{32.0} & \SW{41.5} & \SW{73.4} & 38.9 & 47.5 \\% & 23.3 \\
    \revision{\system{FT-Res}}   \hfill{\footnotesize[+12.4m]}  & 37.3 & \SB{57.9} & \SB{53.9} & 33.8 & \SB{46.7} & \SB{90.2}  & \SB{42.3} & \SB{53.3} \\ % & 20.5\\ \hline
    \system{MDL-Res} \hfill{\footnotesize[+12.4m]}    & 37.9 & \SB{56.0}  & \SB{51.2}   & 33.5   &  44.4  & \SB{88.3} & 42.0 & \SB{51.9} \\%  & \SW{21.2} \\
%     \hfill MDL Res (gen)    & 37.7 & 51.0 & 34.0 & 30.4 & 34.2 & 15.2 & 36.4 & 33.7\\
%    \system{MDL Gated} & 37.7 & 56.5 & 53.2 & 34.1 & 44.6 & 90.7 & 42.3 & 53.3&\\
     \hline \hline
    \system{Mixed-Nat-RNN} \hfill{\footnotesize[51m]}  & 36.8 & 53.8 & 47.2 & 30.0 & 35.7 & 60.2  & 39.2  & 44.0 \\
    \hline
    \system{WDCMT}  \hfill{\footnotesize[73m]} & 36.0 & 53.3 & \SB{48.8} & 31.1 & \SB{38.8} & \SW{58.5} & 39.0 & 44.4 \\ % & 20.4 \\
    \hline
  \end{tabular}
  \caption{Translation performance of MDMT systems \revision{based on the same Transformer (top) or RNN (bottom) architecture. The former contains 65m parameters, the latter has 51m. For each system, we report the number of additional domain specific parameters,}  BLEU scores for each domain, domain-weighted (w\domain{avg}) and unweighted (\domain{avg}) averages. \revision{For weighted-averages, we take the domain proportions from Table~\ref{tab:Corpora}}. Boldface denotes significant gains with respect to \system{Mix-Nat} (or \system{Mix-Nat-RNN}, for WDCMT), underline denotes significant losses.}
  \label{tab:performance}
  % \fyDone{Fill the table with all results, including a comparison with *RNNs* for wcmd}
  \fyDone{Do we have significancy tests for averages?} %\fyTodo{Add tests wrt to RNN}
\end{table*}

@@

All MDMTs (except \system{DM} and \system{ADM}) slightly improve over \system{Mixed-Nat}(for most domains), but these gains are rarely significant. \revision{Among systems using an extra domain feature, \system{DC-Tag} has a small edge over \system{DC-Feat} and also requires less parameters; it also outperforms \system{TTM}, which however uses predicted rather than gold domain tags. \system{TTM} is also the best choice among the systems that to not use domain tags in inference.} \revision{The best contenders overall are  \system{FT-Res} and \system{MDL-Res}, which significantly improve over \system{Mixed-Nat} for a majority of domains, and are the only ones to clearly fulfill [P1-LAB];} \system{WDCMT} also improves on three domains, but regresses on one. The use of a dedicated adaptation module thus seems better than feature-based strategies, \revision{but yields a large increase of the number of parameters.} The effect of the adaptation layer is especially significant for small domains (\domain{bank}, \domain{it} and \domain{rel}).

@@

\begin{table*}
  \centering% \small
  \begin{tabular}{|p{1.8cm}|*{10}{r|}} \hline
    % &&&&&& \\
    \hfill Set-up & \multicolumn{2}{c|}{Split} &  \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Merge} & \multicolumn{2}{c|}{Wrong} \\ % \hline
     Model \hfill & \multicolumn{2}{c|}{\domain{med} \footnotesize{(0.5 / 0.5)}} &  \multicolumn{2}{c|}{\domain{med} {\footnotesize (0.25 / 0.75)}} & \multicolumn{2}{c|}{\domain{law} {\footnotesize (0.5 / 0.5)}} & \multicolumn{2}{c|}{\domain{bank}+\domain{law}} &  \multicolumn{1}{c|}{\domain{rnd}} &  \multicolumn{1}{c|}{\domain{new}}\\ \hline
    & \domain{med}$_1$ & \domain{med}$_2$ & \domain{med}$_1$ & \domain{med}$_2$ &  \domain{bank}$_1$ & \domain{bank}$_2$ & \domain{bank} & \domain{law}   & \domain{all} & \domain{News} \\
    \system{FT-Full}      & -0.1 & -0.6 & \SW{-1.5} & -0.2& \SW{-2.3} & \SW{-5.1} &\SW{-1.6} & \SW{-1.4}& \SW{-19.6} & \SW{-3.3}\\% [32.5]
    \system{DC-Tag}     & -0.2 & -0.3& +\SB{0.1}  & +0.2& -0.4 & -0.4 & -0.5 & -0.4 & \SW{-13.4} & \SW{-1.7}\\% [35.9]
    \system{DC-Feat}    & -0.5 & 0.0 & +\SB{0.3}   & +0.3 & +0.3 & +0.3 & +0.3 & +0.1 & \SW{-14.2} &\SW{-1.8}\\ % [34.9] 
    \system{LDR}           & +0.1 & +0.1 & +0.4 & +0.4 & 0.0 &  0.0 &  0.0 & +0.1& \SW{-12.0} & \SW{-1.4}\\ % [37.0]
    \system{TTM} (*)        & -0.2 &  -0.2 & -0.2 & -0.2 & -0.3 &-0.3 &  0.0 & -0.3 & 0.0 & -0.1\\
%    \system{MDL Gated} & & & & & & & & &  \\
    \system{DM} (*)           & -0.3   & -0.3  & +0.4 & +0.4 & +0.3 & +0.3 & +0.9 & +0.1 & 0.0 &-0.9\\
    \system{ADM} (*)        & +0.6   & +0.6 & +0.4 & +0.4 & +0.4 & +0.4 &  +0.1 & -0.4 & 0.0&-0.2\\
    \revision{\system{FT-Res}}   & -0.1   & -0.4 & -0.3 &-0.3 & \SW{-2.2} & \SW{-2.9} & \SW{-2.4} & -\SW{3.2} & \SW{-13.3} & \SW{-3.0}\\ % [31.8]
    \system{MDL-Res}   & -0.2   & -0.1 & +\SB{0.2} &+0.0 & -0.9 & -0.9 & +0.7 & -0.3 & \SW{-18.6} & \SW{-1.3}\\ % [31.8]
    \system{WDCMT} (*)     & -0.0    & -0.0  & +0.2 & +0.2  & +0.8 & +0.8  & -0.4 & -0.8 & 0.0 & +0.2 \\
    \hline
  \end{tabular}
  \caption{Translation performance with variable domain definitions. In the Split/Merge experiments, we report BLEU differences for the related test set(s). Underline denotes significant loss when domains are changed wrt.\ the baseline situation; bold for a significant improvement over \system{FT-Full}; (*) tags systems ignoring test domains.
    \fyDone{Check wrong and significance of diff for ``old''}\fyDone{How about wrong ?}\jcTodo{FTres results are odd... split LAW 0.5}
  }
  \label{tab:redomains}
\end{table*}

Our findings can be summarized as follows. For the split experiments, we see small variations that can be positive or negative compared to the baseline situation, but these are hardly significative. All systems show some robustness with respect to fuzzy domain boundaries; this is mostly notable for \system{ADM}, suggesting that when domain are close, ignoring domain differences is effective. In contrary, \system{FT-Full} incurs clear losses across the board, especially for the small data condition \cite{Miceli-barone17regularization}. Even in this very favourable case however, very few MDMT systems are able to significantly outperform \system{FT-Full} and this is only observed for the smaller part of the \domain{med} domain. The merge condition is hardly different, with again large losses for \system{FT-full} \revision{and \system{FT-Res}}, and small variations for all systems. We even observe some rare improvements with respect to the situation where we use actual domains.\fyDone{More comments ?}
